Sediment transport capacity varies more in subglacial systems compared to fluvial ones

### 2023-02-21 theory.tex
new figs

              \textbf{Parameters and Constants}  & & &\\
              Gravitational constant&$g$& $-9.81$&$\mathrm{m\,s^{-2}}$\\
              Density of water & $\rho_w$& $1000$ & $\mathrm{kg\,m^{-3}}$ \\
              Density of ice & $\rho_i$& $900$ & $\mathrm{kg\,m^{-3}}$ \\
              Kinematic viscosity of water &$\nu$& $10^{-4}$& $\mathrm{m^2\,s^{-1}}$\\
              Hooke angle of channel & $\beta$ & $\frac{\pi}{2}$ & \unit{rad}\\
              Flotation fraction & $f_f$&$0.7$& $\mathrm{(-)}$\\
              Friction factor (glacier) & $f_r$ & $4$ & $\mathrm{(-)}$ \\
              Friction factor (fluvial) & $f_p$ & $3$ & $\mathrm{(-)}$\\
              Gradient of glacier surface & $\frac{\paratial z_{sg}}{\partial x}$ &$0.25$& $\mathrm{(-)}$\\
              Gradient of channel bed (fluvial) &$\frac{\paratial z_c}{\partial x}$ &$0.05$& $\mathrm{(-)}$\\
              Fluvial channel factor & $k$ &$3$ & $\mathrm{m^{-2}\, s}$\\
              Channel geometry exponent &$e$& $\frac{1}{2}$&$\mathrm{(-)}$ \\
              \hline
            \end{tabular}
            \label{table:vpm}
          \end{table}

@@

          The fluvial channel parameterization implements the hydraulics parameterization presented in \citet{tucker1997}.
          Here, the assuming the conservation of mass, sufficiently wide channels so that the hydraulic radius is consistent with flow depth, uniform flow, and the Darcy-Weisbach relationship,
          the shear stress $\tau_f$ at the river bed is represented as
          \begin{linenomath*}
            \begin{equation}
              \label{eq:DW_tau}
              \tau_f=\frac{\rho_w\,g^{\frac{2}{3}}\,f_p^{\frac{1}{3}}}{2}\, \Big(\frac{Q_w}{w_{cf}} \Big)^{\frac{2}{3}} \,\frac{\partial z_c}{\partial x}^{\frac{2}{3}},
            \end{equation}
          \end{linenomath*}
          where $\frac{\paratial z_c}{\partial x}$ is the channel slope, and $f_p$ is the friction factor for fluvial systems.
          Channel width $w_{cf}$ is 
          \begin{equation}
            \label{eq:wcf}
            w_{cf} = k \, Q_w^e,
          \end{equation}
          % 
          where $k$ is a constant and $e$ is an exponent commonly equal to $\frac{1}{2}$ \citep{leopold1953}. Cross-sectional area is 
          \begin{equation}
            \label{eq:Sf}
            S_f= \frac{Q_w}{v_f}.
          \end{equation}
          As in Section~\ref{sect:sub_mode}, the width integrated shear stress is $\tau_{tf}=w_{cf}\,\tau_f$.
          Hydraulic diameter of the channel is given by $D_{hf} = \frac{4\,w_{cf}\,d}{2\,d+w_{cf}}$, with flow depth $d$ determined from knowledge of $S_f$ and $w_{cf}$ in a rectangular channel.

>>>>

      \textbf{Parameters and Constants}  & & &\\
      Gravitational constant&$g$& $-9.81$&$\mathrm{m\,s^{-2}}$\\
      Density of water & $\rho_w$& $1000$ & $\mathrm{kg\,m^{-3}}$ \\
      Density of ice & $\rho_i$& $900$ & $\mathrm{kg\,m^{-3}}$ \\
      Kinematic viscosity of water &$\nu$& $10^{-4}$& $\mathrm{m^2\,s^{-1}}$\\
      Hooke angle of channel & $\beta$ & $\frac{\pi}{2}$ & \unit{rad}\\
      Flotation fraction & $f_f$&$0.7$& $\mathrm{(-)}$\\
      Friction factor (glacier) & $f_r$ & $4$ & $\mathrm{(-)}$ \\
      Friction factor (fluvial) & $f_p$ & $3$ & $\mathrm{(-)}$\\
      Gradient of glacier surface & $\frac{\partial z_{sg}}{\partial x}$ &$0.25$& $\mathrm{(-)}$\\
      Gradient of channel bed (fluvial) &$\frac{\partial z_c}{\partial x}$ &$0.05$& $\mathrm{(-)}$\\
      Fluvial channel factor & $k$ &$3$ & $\mathrm{m^{-2}\, s}$\\
      Channel geometry exponent &$e$& $\frac{1}{2}$&$\mathrm{(-)}$ \\
      \hline
    \end{tabular}
    \label{table:vpm}
  \end{table}

@@

  The fluvial channel parameterization implements the hydraulics parameterization presented in \citet{tucker1997}.
  Here, the assuming the conservation of mass, sufficiently wide channels so that the hydraulic radius is consistent with flow depth, uniform flow, and the Darcy-Weisbach relationship,
  the shear stress $\tau_f$ at the river bed is represented as
  \begin{linenomath*}
    \begin{equation}
      \label{eq:DW_tau}
      \tau_f=\frac{\rho_w\,g^{\frac{2}{3}}\,f_p^{\frac{1}{3}}}{2}\, \Big(\frac{Q_w}{w_{cf}} \Big)^{\frac{2}{3}} \,\frac{\partial z_c}{\partial x}^{\frac{2}{3}},
    \end{equation}
  \end{linenomath*}
  where $\frac{\partial z_c}{\partial x}$ is the channel slope, and $f_p$ is the friction factor for fluvial systems.
  Channel width $w_{cf}$ is 
  \begin{equation}
    \label{eq:wcf}
    w_{cf} = k \, Q_w^e,
  \end{equation}
  % 
  where $k$ is a constant and $e$ is an exponent commonly equal to $\frac{1}{2}$ \citep{leopold1953}. Cross-sectional area is 
  \begin{equation}
    \label{eq:Sf}
    S_f= \frac{Q_w}{v_f}.
  \end{equation}
  As in Section~\ref{sect:sub_mode}, the width integrated shear stress is $\tau_{tf}=w_{cf}\,\tau_f$.
  Hydraulic diameter of the channel is given by $D_{hf} = \frac{4\,w_{cf}\,d}{2\,d+w_{cf}}$, with flow depth $d$ determined from knowledge of $S_f$ and $w_{cf}$ in a rectangular channel.
